Turbulence in compact to giant HII regions

### 2022-02-08 strucfunc_paper.tex
Add some discussion of the largest scales

In order to capture these two behaviors,
We therefore propose the following 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We use equation \eqref{eq:functional} to determine the structure function
from this model autocorrelation function.
The resultant model structure function has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B(r_0) = \sigma^2\);
 \item Large scales: \(B(r) \to 2 \sigma^2\) for \(r \gg r_0\).
\end{enumerate}
In a previous paper, we used a different functional form
\citetext{See Fig.~13 of \citealp{arthur2016turbulence}}:
\(C(r) = 1/[1+(r/r_{0})^{m}]\), as proposed in \citet{1984ApJ...277..556S},
which behaves identically to equation~\eqref{eq:new-correlation-form}
in the first two regimes, but is more gradual in its approach
to the large-scale asymptote of \(2 \sigma^2\).
However, we find that equation~\eqref{eq:new-correlation-form}
provides a much improved fit to the observed structure functions
of our sample regions.

@@

\subsection{Effects of observational limitations}
\label{sec:effect-observ-limit}

@@

\subsection{Limitations of the model structure function}
\label{sec:limit-model-struct}

>>>>

In order to capture these two behaviors,
We therefore propose the following idealized 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We use equation \eqref{eq:functional} to determine the structure function
from this model autocorrelation function.
The resultant model structure function has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B(r_0) = \sigma^2\);
 \item Large scales: \(B(r) \to 2 \sigma^2\) for \(r \gg r_0\).
\end{enumerate}
In a previous paper, we used a different functional form
\citetext{See Fig.~13 of \citealp{arthur2016turbulence}}:
\(C(r) = 1/[1+(r/r_{0})^{m}]\), as proposed in \citet{1984ApJ...277..556S},
which behaves identically to equation~\eqref{eq:new-correlation-form}
in the first two regimes, but is more gradual in its approach
to the large-scale asymptote of \(2 \sigma^2\).
However, we find that equation~\eqref{eq:new-correlation-form}
provides a much improved fit to the observed structure functions
of our sample regions (see following section).

@@

\subsubsection{Effects of observational limitations}
\label{sec:effect-observ-limit}

@@

\subsubsection{Additional effects omitted from the model structure function}
\label{sec:limit-model-struct}

For separations that are comparable to the diameter \(D\) of the \hii{} region,
then the supposition of homogeneity must break down.
For instance, if the amplitude of the velocity fluctuations is higher
in the core of the region than in the outskirts,
then the autocorrelation function will be U-shaped
since all separations with \(r > D/2\) must be between two points in the outskirts,
which will tend to be relatively well correlated simply because both velocities
will be close to the mean.
This yields a corresponding downturn in the structure function at the largest scales.

Another example is if there were a periodic velocity fluctuation,
with spatial wavelength \(\lambda\),
then the autocorrelation function would become negative for \(r \approx \lambda/2, 3 \lambda / 2, \dots\),
which yields periodic peaks in the structure function.
Neither of these effects can be captured by our model structure function,
which assumes that the autocorrelation is strictly positive
and monotonically decreasing with \(r\).

At the very smallest scales, the autocorrelation function is predicted to
scale quadratically with \(r\)
